---
title: "BIOL 432 - R-eproducibility"
author: "Roshael Chellappah (20103016)"
date: "26/01/2022"
output:
  html_document: default
  pdf_document: default
---

**Project Information**  
git hub username: RoshaelC  
git hub repository: https://github.com/RoshaelC/r-eproducibility.git  

## Project Set Up
```{r echo=FALSE}
library(dplyr)
data <- read.csv("./InputData/FallopiaData.csv")
```

## Dataset Prep
Remove rows with "Total" biomass < 60
```{r}
MyData <- subset(data, Total > 60)
```

Reorder the columns in the order "Total", "Taxon", "Scenario", "Nutrients" and remove other columns
```{r}
colnames(MyData) #identify what the current column names are

MyData <- transmute(MyData, Total, Taxon, Scenario, Nutrients) #transmute = mutate() + select()
colnames(MyData)
```

Replace "Total" with new column with "TotalG", converting values from mg to g
```{r}
MyData <- transmute(MyData, TotalG = Total*0.001, Taxon, Scenario, Nutrients) # 1 mg is 0.001 g
```

## Custom Function  
Write a custom function that will take two inputs from the user:  
1. a vector of data to process (e.g., column from a data.frame object)  
2. a string that defines what calculation to perform  
  - if string #2 is "Average" then calculate the average value for the column named in vector #1  
  - if s2 is "Sum" then calculate the sum of values for the column named in v1  
  - if s2 is "Observations" then count the number of observed values for the column named in v1  
  - if s2 is anything else, then outut an error to the user  
```{r}

my.function <- function(datacol = 0, calc = 0){
  cat("\n**User input** \nvector data:", datacol, "\ncalculation:", calc, "\n")
  
  if (calc == "Average"){
    cat("\nCalculating average...\n")
    mean <- mean(datacol)
    return(average = mean)
  }
  
  else if (calc == "Sum"){
    cat("\nCalculating sum...\n")
    sumvector <- sum(datacol)
    return(sum = sumvector)
  }
  
  else if (calc == "Observations"){
    cat("\nCalculating number of observations...\n")
    obs <- NROW(datacol)
    return(observations = obs)
  }
  
  else{
    cat("\nUnrecognized calculation, please use 'Average', 'Sum' or 'Observations'...\n")
  }
}
```

  
Write some R code that uses your function to count the total number of observations in the "Taxon" column
```{r}
my.function(datacol = MyData$Taxon, calc = "Observations")
```


Write some R code that uses your function to calculate the average TotalG for each of the two Nutrient concentrations
```{r}

WData <- MyData %>% 
  group_by(Nutrients) %>% #groups MyData by Nutrient values 'high' and 'low'
  summarize("Average TotalG" = my.function(datacol = TotalG, calc = "Average")) #summarizes the results of my.function() calculating TotalG averages for 'high' vs. 'low' Nutrient observations

WData
```

Write (i.e., save) the new data to a file called "WrangledData.csv" in the Output folder.
```{r}
write.csv(WData, "./Output/WrangledData.csv")
```

  
  
  
  
  