---
title: "Regex.Rmd"
author: "Roshael Chellappah (20103016)"
date: "02/02/2022"
output: html_document
---

**Project Set-Up**  
git hub username: RoshaelC  
git hub repository: https://github.com/RoshaelC/r-eproducibility.git  

```{r}
library(dplyr)
getwd()
```

# Part I: Data Science

1. Add new coloumn called "Sp" that shortens the genus name in the "Organism" column to only the first letter and period (i.e., Homo sapiens -> H. sapiens)
```{r}
MData <- mutate(
  read.csv("C:/Users/rosch/Documents/BIOL 432/Week 1 - Introduction/A1_CHELLAPPAH_ROSHAEL.csv"), 
  Sp = gsub("[a-z]\\w+\\s", "\\. ", Organism))

# gsub() used to find and replace data
# [a-z] identifies all lower case letters (disregards upper case)
# \\w+ identifies strings of any character that is a letter or digit 
# \\s identifies spaces
# \\. replaces the identified string characters with a "."
```

2. Create a new dataset BUT with "Sp" column where "Organism" column is, and remove "Organism" column
```{r}
MData <- transmute(MData, Sp, Limb.width, Limb.length, Observer)
```

3. Save the dataset as a new file called "MeasShort.csv"
```{r}
write.csv(MData, "./MeasShort.csv")
```

# Part II: Bash
See .txt file "A4_Chellappah_Roshael.txt"